---
title: "Homework 5"
output: github_document
author: Sushupta Vijapur (smv2138)
---
```{r}
library(tidyverse)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

```{r}

homicide_df <- 
  read_csv("hom_data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age), 
    resolved = case_when(
      disposition == "Closed without arrest" ~ 0, 
      disposition == "Open/No arrest" ~ 0, 
      disposition == "Closed by arrest" ~ 1,
    )
  ) %>% 
  filter(
    city_state != "Tulsa, AL", 
    victim_race %in% c("White", "Black")) %>% 
  select(city_state, resolved, victim_age, victim_race, victim_sex)
```



Start with one city

```{r}
baltimore_df <-
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolved ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df, 
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate), 
    CI_lower = exp(estimate - 1.96 * std.error), 
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)

```



Let's try this across cities
```{r}
model_results_df <-
homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())), 
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate), 
    CI_lower = exp(estimate - 1.96 * std.error), 
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))

```

```{r}
model_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Problem 2
compare 3 models using CV
build a model (open ended)
start with checking for cross validation
Porbably want to do some work with factor variables 
Find some residuals
```{r}
baby_df = 
  read_csv("./hom_data/birthweight.csv")
```

```{r}
model_fit = lm(bwt ~ gaweeks, data = baby_df)
```

```{r}
baby_df %>% 
  modelr::add_residuals(model_fit) %>% 
  ggplot(aes(x = gaweeks ,y = resid)) +
  geom_point()
```


## Problem 3

use bootstrap to get distribution of parameters you're interested in
fit linear model of max emp against min temp
r sq value and another random param ()
